Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-17 papers/EMNLP2019/analysis.tex
Figures->figures; results in modeling
new table with cool examples

\gbt{Super-interesting results.}
Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e. variants of the original VG class. 
Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.  
Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
%

\paragraph{Qualitative Analysis}

\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.

\begin{table}
\small
\begin{tabular}{lp{4.8cm}r}
\toprule
VG name &  top5 MN names &  n$_{obj}$  \\
\midrule
\multicolumn{3}{c}{\it Canonical VG names with max agreement in MN}\\
 giraffe &  giraffe (96.8), animal (1.2), zebra (0.4), camel (0.3), pole (0.1) &  915 \\
 zebra &  zebra (96.3), animal (1.0), giraffe (0.9), horse (0.2), microwave (0.2) &  461  \\
 cat &  cat (94.8), animal (0.9), kitten (0.8), dog (0.4), laptop (0.2) &  754\\
\midrule
\multicolumn{3}{c}{\it Canonical VG names with min agreement in MN}\\
 booth &  booth (19.3), table (12.3), phone booth (9.8), bench (6.7), building (4.4) &  11 \\
 cabbage &  cabbage (21.4), lettuce (17.0), hotdog (11.9), food (10.7), salad (10.4) &  9 \\
 robe &  robe (22.1), shirt (16.8), jacket (13.3), dress (5.7), clothing (3.2) &  19 \\
  \midrule
  \multicolumn{3}{c}{\it Non-canon. VG names with max agreement in MN}\\
 sedan &  car (88.4), wheel (3.1), vehicle (2.3), automobile (1.3), dog (0.8) &  11 \\
 pony &  horse (83.9), pony (9.1), animal (2.9), donkey (1.1), cow (1.1) &  8 \\
 necktie &  tie (81.4), necktie (10.2), shirt (4.6), ties (1.5), jacket (0.5) &  11 \\
 \midrule
   \multicolumn{3}{c}{\it Non-canon. VG names with min agreement in MN}\\
 shelter &  umbrella (9.7), shelter (8.8), roof (8.0), tent (7.1), building (6.8) &  10 \\
 bath &  shower (13.3), elephant (9.9), birdbath (8.1), water (7.2), trough (7.2) &  10 \\
 vegetable &  food (15.7), broccoli (13.1), sandwich (10.6), salad (9.3), pizza (7.8) &  25 \\
\bottomrule
\end{tabular}
\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in ManyNames (MN; percentages shown in brackets). ``Canonical'' means that the VG name is the top name in MN, and non-canonical vice versa.}
\label{tab:qual}
\end{table}

\gbt{The non-canon. VG names suggest that people prefer more general names (``car $>$ sedan'', ``horse $>$ pony'', ``tie $>$ necktie''). Could be due to lexical availability (more general \ra more frequent \ra more available). This could be verified (using frequency). Hypothesis: In cases where top name != VG, the VG name is less general. Could be also a more general hypothesis: see if people prefer more frequent names in general.}
\cs{@Table~\ref{tab:qual} (just wrt presentation) The most interesting blocks are 2 and 3 (canonical VG with min agr.; non-canonical with max agr.)}

>>>>

%\gbt{Super-interesting results.}
Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e. variants of the original VG class. 
Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.  
Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
%\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
%

\subsection{Variation and WordNet}

Previous work on large-scale collections of labels or names of objects has (explicitly or implicitly) assumed that once naming data is canonical, linguistic alternatives of the canonical name can simply be retrieved from existing taxonomies like e.g.\ WordNet. 
%If this was indeed the case, it would be feasible (and probably even desirable) to canonicalize object names during dataset collection, without loosing too much information about linguistic variations in natural object naming scenarios (like e.g.\ referring expression generation).
Hence, in this section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.
%In this section, we take a closer look at the lexical variation we observe in our data set. 
We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
The naming variants can be grouped according to their lexical relation, as follows:

\begin{itemize}
\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
\item \textbf{hyponymy}: e.g.\ man vs. person
\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
\item \textbf{no relation}: e.g.\  desk vs. apple
\end{itemize}

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 word-not-covered &  10.6 &  2.6 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in MN to annotated VG synset, averaged over synsets}
\label{tab:rel}
\end{table}

Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).

We use WordNet to extract lexical relations between the naming variants in our data set.
Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below). Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy. 
For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
\sz{should we call this co-hyponymy or co-hierarchical relation?}

\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}

Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet.
Both in terms of their types and token frequency, the naming variants that instantiate a (loose) co-hyponymy relation are by far the most frequent.
\sz{discuss in more detail, discuss: to what extent is this an artefact of WordNet?}
This is really interesting: most research on object naming, to date, has focussed on hyponymy/hypernymy, i.e. variation that relates to hierarchical relations between object names.
Our data suggests that co-hierarchical variation is really important too.

%\subsection{Qualitative Analysis}

%\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.

%\begin{table}
%\small
%\begin{tabular}{lp{4.8cm}r}
%\toprule
%VG name &  top5 MN names &  n$_{obj}$  \\
%\midrule
%\multicolumn{3}{c}{\it Canonical VG names with max agreement in MN}\\
% giraffe &  giraffe (96.8), animal (1.2), zebra (0.4), camel (0.3), pole (0.1) &  915 \\
% zebra &  zebra (96.3), animal (1.0), giraffe (0.9), horse (0.2), microwave (0.2) &  461  \\
% cat &  cat (94.8), animal (0.9), kitten (0.8), dog (0.4), laptop (0.2) &  754\\
%\midrule
%\multicolumn{3}{c}{\it Canonical VG names with min agreement in MN}\\
% booth &  booth (19.3), table (12.3), phone booth (9.8), bench (6.7), building (4.4) &  11 \\
% cabbage &  cabbage (21.4), lettuce (17.0), hotdog (11.9), food (10.7), salad (10.4) &  9 \\
% robe &  robe (22.1), shirt (16.8), jacket (13.3), dress (5.7), clothing (3.2) &  19 \\
%  \midrule
%  \multicolumn{3}{c}{\it Non-canon. VG names with max agreement in MN}\\
% sedan &  car (88.4), wheel (3.1), vehicle (2.3), automobile (1.3), dog (0.8) &  11 \\
% pony &  horse (83.9), pony (9.1), animal (2.9), donkey (1.1), cow (1.1) &  8 \\
% necktie &  tie (81.4), necktie (10.2), shirt (4.6), ties (1.5), jacket (0.5) &  11 \\
% \midrule
%   \multicolumn{3}{c}{\it Non-canon. VG names with min agreement in MN}\\
% shelter &  umbrella (9.7), shelter (8.8), roof (8.0), tent (7.1), building (6.8) &  10 \\
% bath &  shower (13.3), elephant (9.9), birdbath (8.1), water (7.2), trough (7.2) &  10 \\
% vegetable &  food (15.7), broccoli (13.1), sandwich (10.6), salad (9.3), pizza (7.8) &  25 \\
%\bottomrule
%\end{tabular}
%\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in ManyNames (MN; percentages shown in brackets). ``Canonical'' means that the VG name is the top name in MN, and non-canonical vice versa.}
%\label{tab:qual}
%\end{table}

\begin{figure*}
\begin{minipage}[b]{0.5\linewidth}
{\footnotesize
\setlength{\tabcolsep}{1pt}
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}
%\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343219_926143_supercat_unique.png}}  MN: desktop &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
%\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2350360_1042111_supercat_unique.png}} MN: table  &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2389358_1261752_singleton_obj.png}}  MN: seat &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
\multicolumn{4}{c}{\textbf{VG: sandwich}}\\
 \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), food (5), burger (2), hamburger (2), meal (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} food (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), food (7), bun (4), sandwich (3), bread (2)\\ 
\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20), building (11)  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\ 
\multicolumn{4}{c}{\textbf{VG: bed}}\\ 
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2321254_3438076_singleton_obj.png}} bed (36)  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2324306_3412337_singleton_obj.png}}  bed (16), bench (6), crib (5) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2342811_3485104_singleton_obj.png}}  bed (17), book (6), table (4), toy (3), bible (2), doll (2) & 
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 
\multicolumn{4}{c}{\textbf{VG: batter}}\\
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), person (3), baseball player (2) &
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), baseball player (7), batter (5), player (3), helmet (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), baseball player (4), player (4), man (3), child (3), batter (3), dress (2), kid (2)&
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), player (5), shoe (4), bat (4), person (4), legs (4), baseball player (3), hitter (2)\\ 
\multicolumn{4}{c}{\textbf{VG: robe}}\\
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), bathrobe (5) &
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), sweater (9), coat (3), doll (3), toy (3), shirt (2), bear (2), robe (2)\\

\end{tabular}

}
\end{minipage}

 \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set}
\end{figure*}

%\gbt{The non-canon. VG names suggest that people prefer more general names (``car $>$ sedan'', ``horse $>$ pony'', ``tie $>$ necktie''). Could be due to lexical availability (more general \ra more frequent \ra more available). This could be verified (using frequency). Hypothesis: In cases where top name != VG, the VG name is less general. Could be also a more general hypothesis: see if people prefer more frequent names in general.}
%\cs{@Table~\ref{tab:qual} (just wrt presentation) The most interesting blocks are 2 and 3 (canonical VG with min agr.; non-canonical with max agr.)}
